Plot responses to model covariates to inform threshold choices for VOCC

### 2019-08-06 analysis/VOCC/2-biomass-trends.Rmd
minor edits to model building rmds

Species
```{r}
# # Species run so far...
species <- "Arrowtooth Flounder"
 species <- "Pacific Cod"
species <- "Sablefish"
 species <- "Silvergray Rockfish"
species <- "Lingcod"
 species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
 species <- "Pacific Ocean Perch"
 species <- "Yelloweye Rockfish"
```

@@

  max_raster <- quantile(adult_predictions$est_exp, .999)
  max_adult <- signif(max(adult_predictions$est_exp), digits = 2)

>>>>

Species
```{r}
# # Species run so far...
 species <- "Arrowtooth Flounder"
#  species <- "Pacific Cod"
# species <- "Sablefish"
#  species <- "Silvergray Rockfish"
# species <- "Lingcod"
#  species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```

@@

  max_raster <- quantile(adult_predictions$est_exp, 0.999)
  max_adult <- signif(max(adult_predictions$est_exp), digits = 2)

### 2019-08-06 analysis/VOCC/3-variable-response-plots.Rmd
minor edits to model building rmds

Species
```{r}

# # Species run so far...
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
 species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds
# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"

# species <- "Yelloweye Rockfish"
# species <- "Arrowtooth Flounder"

>>>>

Species
```{r}
#species <- params$species
# # Species run so far...
species <- "Arrowtooth Flounder"
# species <- "Pacific Cod"
# species <- "Sablefish"
# species <- "Silvergray Rockfish"
# species <- "Lingcod"
# species <- "North Pacific Spiny Dogfish" # note: using all data for maturity thresholds

# species <- "Quillback Rockfish"
# species <- "Pacific Ocean Perch"
# species <- "Yelloweye Rockfish"
```
